Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-07-08 analysis/paper/paper.Rmd
Label subheading "Supplementary Tables"
Escape special characters

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 to predict two responses with publishing journal, as the journals’ abbreviation, the formula took the form: response ~ abbreviation (model 1: code_availability ~ abbreviation and model 2: data_availability ~ abbreviation) and the models included assignee as a random effect (formula: ~1 | assignee).
Models 3 and 4 to predict the two responses with year (formula: response ~ year) and the models included abbreviation and assignee as random effects (formula: list(~1 | abbreviation, ~1 | assignee)). 
Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response ~ IF_5year and included assignee as random effect (formula: ~1 | assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.

@@

When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterranea* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (> 0), 90.61% of being significant (> 0.05), and 78.94% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 25478).
The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (> 0), 99.42% of being significant (> 0.05), and 97.73% of being large (> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24986).

@@

## Tables

>>>>

Six models were applied, with half predicting the response of code availability and the other half predicting data availability.
Models 1 and 2 to predict two responses with publishing journal, as the journals' abbreviation, the formula took the form: response \~ abbreviation (model 1: code_availability \~ abbreviation and model 2: data_availability \~ abbreviation) and the models included assignee as a random effect (formula: \~1 \| assignee).
Models 3 and 4 to predict the two responses with year (formula: response \~ year) and the models included abbreviation and assignee as random effects (formula: list(\~1 \| abbreviation, \~1 \| assignee)).
Models 5 and 6 to predict the two responses with IF_5year the formula took the form: response \~ IF_5year and included assignee as random effect (formula: \~1 \| assignee) without journal as a random effect to mitigate correlation between impact factor and the journal of publication.

@@

When predicting the availability of data availability as compared with *Phytopathology*, publications in two journals, *Phytopathologia Mediterranea* and *Molecular Plant Pathology*, can be considered clearly more likely to share data than publications in *Phytopathology*, but no effects were detectable in any other journal title (\@ref(fig:journal-parameters)B, Figure S2, Table S2).
The effect of *Molecular Plant Microbe Interactions* (Median = 0.67, 95% CI [-0.28, 1.57]) has a 92.15% probability of being positive (\> 0), 90.61% of being significant (\> 0.05), and 78.94% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 25478).
The effect of *Phytopathologia Mediterranea* (Median = 1.25, 95% CI [0.32, 2.15]) has a 99.58% probability of being positive (\> 0), 99.42% of being significant (\> 0.05), and 97.73% of being large (\> 0.30).
The estimation successfully converged (Rhat = 1.000) and the indices are reliable (ESS = 24986).

@@

## Supplementary Tables
